### 2012-10-30 4.tex
more new graphs

\noindent
\citet{Pierrehumbert1994} does not discuss a constraint against adjacent obstruents disagreeing in voice. However, the vast majority of medial obstruents clusters in simplex wors are either uniformly voiced, as in \emph{hu}[z.b]\emph{and}, or uniformly voiceless, as in or \emph{rha}[p.s]\emph{osdy}. Hetero-voiced clusters, like those in \emph{a}[b.s]\emph{inth} and \emph{a}[s.b]\emph{estos} are rare in comparison.

>>>>

\noindent
\citet{Pierrehumbert1994} does not discuss a constraint against adjacent obstruents disagreeing in voice. As shown in Table \ref{ovatab} however, the vast majority of medial obstruents clusters in simplex words are either uniformly voiced, as in \emph{hu}[z.b]\emph{and}, or uniformly voiceless, as in or \emph{rha}[p.s]\emph{osdy}. Hetero-voiced clusters, like those in \emph{a}[b.s]\emph{inth} and \emph{a}[s.b]\emph{estos} are rare in comparison.
